\documentclass{article}
\usepackage{fullpage}
\usepackage{hyperref}
\title{CISP1020 - Midterm Exam Review Questions}
\date{Spring 2020}

\begin{document}
\maketitle
\begin{enumerate}
\item What is a function?
\item How do you declare a function? What elements are needed?
\item What is a function prototype?
\item Be able to write code which defines a function and uses it to
solve a problem.
\item What is a struct, and how do you declare one?
\item Be ale to define a struct and use it to solve a problem.
\item What is the main difference between structs in C and C++?
\item What is a C-String?
\item How do C-Strings differ from C++ strings?
\item How are new types created in C?
\item What is a pointer?
\item Are pointers and array names the same thing?  How are they
alike? How do they differ?
\item What is a header file? What sorts of things do you put in
a header file?
\item How do you protect a header file so that its contents are only
included one time?
\item What is a Makefile?
\item Be able to create a simple Makefile.
\item How are command line arguments retrieved inside a program?
\item What is recursion?
\item What two cases are needed in a recursive function?
\item Be able to write a recursive function to solve a problem.
\item How do you dynamically allocate variables in C++?
\item How do you dynamically allocate an array in C++?
\item How do you deallocate variables in C++?
\item How do you deallocate arrays in C++?
\item How do you dynamically allocate memory in C?
\item How do you deallocate memory in C?
\item Be able to write code which uses dynamic memory in both C and
C++.
\item What is an enumerated type?  How do you declare them?
\item What is a linked list?
\item What is a singly linked list?
\item What is a doubly linked list?
\item Be able to perform/code various linked-list operations such as
insert, delete, and traversing the list.
\item What are the main advantages of a linked list over an array?
\item What is a stack?
\item How are stacks implemented using arrays?
\item What is a queue?
\item How are queues implemented using arrays?
\item How are queues implemented using linked lists?
\item What is an object?
\item What is a class, and how does it relate to objects?
\item What do the modifiers public, protected, and private do?
\item What is inheritance?
\item What is polymorphism?
\item Be able to write a class definition and use your class to solve
a problem.
\item How are classes defined and implemented? (what goes in a .h and
a .cpp file?)
\end{enumerate}
\end{document}
